### 2021-03-09 paper.Rmd
working on initial example

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    email: stuart.a.lee@monash.edu
  - name: Ursula Laa 
    affiliation: University of Natural Resources and Life Sciences
    address:  |
      | Institute of Statistics,
      | University of Natural Resources and Life Sciences
    email:  ursula.laa@boku.ac.at
  - name: Natalia da Silva
    address: |
      | Instituto de Estadística (IESTA), 
      | Universidad de la República
    affiliation: Universidad de la República
    email: natalia@iesta.edu.uy
  - name: Nicholas Spyrison
    address: |
      | Faculty of Information and Technology 
      | Monash University
    affiliation: Monash University
    email: nicholas.spyrison@monash.edu
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: dicook@monash.edu
  - name: Earo Wang
    address: |
      | Department of Statistics,
      | The University of Auckland
    affiliation: The University of Auckland
    email: earo.wang@auckland.ac.nz
  - name: H. Sherry Zhang
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: huize.zhang@monash.edu
title:
  formatted: "An Overview of Tours for Dynamic Visualisation of High-dimensional Data"
abstract: > 
  Abstract goes here.
keywords:
  formatted: ["tours", "data visualisation"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

> figure 1 illustrating tour views vs nonlinear dimension reduction for Stuart's cluster example

>>>>

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    email: stuart.a.lee@monash.edu
  - name: Ursula Laa 
    affiliation: University of Natural Resources and Life Sciences
    address:  |
      | Institute of Statistics,
      | University of Natural Resources and Life Sciences
    email:  ursula.laa@boku.ac.at
  - name: Natalia da Silva
    address: |
      | Instituto de Estadística (IESTA), 
      | Universidad de la República
    affiliation: Universidad de la República
    email: natalia@iesta.edu.uy
  - name: Nicholas Spyrison
    address: |
      | Faculty of Information and Technology 
      | Monash University
    affiliation: Monash University
    email: nicholas.spyrison@monash.edu
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: dicook@monash.edu
  - name: Earo Wang
    address: |
      | Department of Statistics,
      | The University of Auckland
    affiliation: The University of Auckland
    email: earo.wang@auckland.ac.nz
  - name: H. Sherry Zhang
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: huize.zhang@monash.edu
title:
  formatted: "An Overview of Tours for Dynamic Visualisation of High-dimensional Data"
abstract: > 
  Abstract goes here.
keywords:
  formatted: ["tours", "data visualisation", "high-dimensional data", "data science", "exploratory data analysis"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

\begin{figure*}[htp]
         \includegraphics[width=0.5\textwidth]{figures/cluster_example_r.pdf}
     \vfill
   \begin{minipage}{\linewidth}     
   \centering
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_tour1_r.pdf}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_tour2_r.pdf}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_tour3_r.pdf}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_tour4_r.pdf}
   \end{minipage}%
\caption{Comparison of structure perception between nonlinear dimension reduction using t-SNE (A) and projections seen during a tour (B.1-4). There are six clusters, as seen in the t-SNE view, but the relative distance between the clusters is extremely varied. This can be seen in the tour projections. The two green clusters are spherical in shape, and very distance from the brown clusters. Three of the brown clusters are very close to each other (just visible in B.1), and all brown clusters are elliptical. The tour provides a more accurate rendering of the clusters in the high-dimensional space, and complements what is learned from the dimension reduction.}
\label{fig:tsne-tour}
\end{figure*}
